---
title: "IRseq example"
author: "jmzeng1314@163.com"
date: "May 10, 2017"
output: html_document
---

## load package and data


```{r}
library(IRseq) 
library(ggplot2)
load('../../keep_IRdata.RData')
names(keep_IRdata)
head(keep_IRdata[[1]])
```

## basic QC for all of the samples

```{r}
qc=do.call(rbind,lapply(keep_IRdata,QC_IR))
colnames(qc)=c('all reads','not qualified','not cdr3 aa')
qc
```

## basic statistic for cdr3 diveristy

```{r}

tmp<-lapply(keep_IRdata,function(x){
  tmp=x[,4]
  tmp=tmp[tmp!='N/A']
  return(c(
    stat_cdr3_diversity(tmp,'d50'),
    stat_cdr3_diversity(tmp,'shannon'),
    stat_cdr3_diversity(tmp,'simpson'),
    stat_cdr3_diversity(tmp,'gini')
  ))
})
diversity=do.call(rbind,tmp)
colnames(diversity)=c('d50','shannon','simpson','gini')
diversity
```


> we can do t.test for cdr3 diversity between case and control group

```{r}
## for d50 index:
plot_t_test(diversity[c(1:7,10),1],diversity[c(8:9,11:15),1] )

## for shanon entropy
plot_t_test(diversity[c(1:7,10),2],diversity[c(8:9,11:15),2] )

# for simpson index
plot_t_test(diversity[c(1:7,10),3],diversity[c(8:9,11:15),3] )

## for gini coefficient 
plot_t_test(diversity[c(1:7,10),4],diversity[c(8:9,11:15),4] )

```

> also we can generate publication qualited figures

```{r,eval=FALSE}
plot_t_test(diversity[c(1:7,10),1],diversity[c(8:9,11:15),1] ,'d50.t.test.png')
plot_t_test(diversity[c(1:7,10),2],diversity[c(8:9,11:15),2] ,'shannon.t.test.png')
plot_t_test(diversity[c(1:7,10),3],diversity[c(8:9,11:15),3] ,'simpson.t.test.png')
plot_t_test(diversity[c(1:7,10),4],diversity[c(8:9,11:15),4] ,'gini.t.test.png')

```

## basic statistcs for v/d/j/cdr3 usage for each sample

> choose the first sample as a example 

```{r}

IR_basic_df=keep_IRdata[[1]]
IR_basic_stat_results <- stat_IR_basic(IR_basic_df)
str(IR_basic_stat_results)
names(IR_basic_stat_results)

plot_usage <- function(dat){
  colnames(dat)=c('x','y')
  p=ggplot(dat,aes(x,y))+geom_bar(stat='identity')+ theme_classic() + scale_y_continuous(expand=c(0,0))+
    theme(text=element_text(face='bold'),axis.text.x=element_text(angle=45,hjust=1,size=10),
          axis.title.x=element_blank())+labs(title='Usage',y="percent")
  print(p)
}
plot_usage(IR_basic_stat_results$v_usage)
plot_usage(IR_basic_stat_results$d_usage)
plot_usage(IR_basic_stat_results$j_usage)
plot_usage(IR_basic_stat_results$cdr3aa_length_usage)
plot_cdr3aa_bar(IR_basic_stat_results$cdr3aa_length_v, 'V segment' )
plot_cdr3aa_bar(IR_basic_stat_results$cdr3aa_length_cdr3aa, 'CDR aa' )
plot_cdr3_stat(IR_basic_stat_results$cdr3aa_stat)
plot_v_j_combination(IR_basic_stat_results$vj_usage_matrix,image_type = 'circle',file_out = 'test.v-j.circle.pdf')
plot_v_j_combination(IR_basic_stat_results$vj_usage_matrix,image_type = 'bubble')

```

## stat for all of the samples:
```{r}
all_results <- lapply(keep_IRdata,stat_IR_basic)
```
> then you can choose two of them to campare their shared CDR3
```{r}
plot_cdr3_paired_comparison(all_results$IgAN10$all_cdr3aa_usage , all_results$IgAN12$all_cdr3aa_usage,
                            'IgAN10','IgAN12')
```

> but It's a little complicated, just for a example.

## generate all of the figures for all of the samples
 
```{r ,eval=FALSE}
lapply(1:length(all_results), function(i){
  this_result <- all_results[[i]]
  this_sample <- names(all_results)[i]

  pdf(paste0(this_sample,".v_usage.pdf"))
  plot_usage(this_result$v_usage);dev.off()
  pdf(paste0(this_sample,".d_usage.pdf"))
  plot_usage(this_result$d_usage);dev.off()
  pdf(paste0(this_sample,".j_usage.pdf"))
  plot_usage(this_result$j_usage);dev.off()
  pdf(paste0(this_sample,".cdr3aa_length_usage.pdf"))
  plot_usage(this_result$cdr3aa_length_usage);dev.off()

  plot_cdr3aa_bar(this_result$cdr3aa_length_v, 'V segment' ,
                  file_out =  paste0(this_sample,".cdr3aa_length_v.pdf"))
  plot_cdr3aa_bar(this_result$cdr3aa_length_cdr3aa, 'CDR aa',
                  file_out =  paste0(this_sample,".cdr3aa_length_cdr3aa.pdf"))
  plot_cdr3_stat(this_result$cdr3aa_stat,
                 file_out = paste0(this_sample,".cdr3aa_stat.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'circle',
                       file_out = paste0(this_sample,".v_j_circle.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'bubble',
                       file_out = paste0(this_sample,".v_j_bubble.pdf"))
})

```


## subset the IR data by IG subtype: IgG,IgA,IgM

> The do the same process as the whole IR data :

```{r,eval=FALSE}
all_results_IgA <- lapply(keep_IRdata,function(x){
  x=subset(x,type='IgA')
  stat_IR_basic(x)
})

lapply(1:length(all_results_IgA), function(i){
  this_result <- all_results_IgA[[i]]
  this_sample <- names(all_results_IgA)[i]
  this_sample <- paste0(this_sample,".IgA")
  pdf(paste0(this_sample,".v_usage.pdf"))
  plot_usage(this_result$v_usage);
  dev.off()
  pdf(paste0(this_sample,".d_usage.pdf"))
  plot_usage(this_result$d_usage);dev.off()
  pdf(paste0(this_sample,".j_usage.pdf"))
  plot_usage(this_result$j_usage);dev.off()
  pdf(paste0(this_sample,".cdr3aa_length_usage.pdf"))
  plot_usage(this_result$cdr3aa_length_usage);dev.off()

  plot_cdr3aa_bar(this_result$cdr3aa_length_v, 'V segment' ,
                  file_out =  paste0(this_sample,".cdr3aa_length_v.pdf"))
  plot_cdr3aa_bar(this_result$cdr3aa_length_cdr3aa, 'CDR aa',
                  file_out =  paste0(this_sample,".cdr3aa_length_cdr3aa.pdf"))
  plot_cdr3_stat(this_result$cdr3aa_stat,
                 file_out = paste0(this_sample,".cdr3aa_stat.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'circle',
                       file_out = paste0(this_sample,".v_j_circle.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'bubble',
                       file_out = paste0(this_sample,".v_j_bubble.pdf"))
})


all_results_IgM <- lapply(keep_IRdata,function(x){
  x=subset(x,type='IgM')
  stat_IR_basic(x)
})
lapply(1:length(all_results_IgM), function(i){
  this_result <- all_results_IgM[[i]]
  this_sample <- names(all_results_IgM)[i]
  this_sample <- paste0(this_sample,".IgM")
  pdf(paste0(this_sample,".v_usage.pdf"))
  plot_usage(this_result$v_usage);dev.off()
  pdf(paste0(this_sample,".d_usage.pdf"))
  plot_usage(this_result$d_usage);dev.off()
  pdf(paste0(this_sample,".j_usage.pdf"))
  plot_usage(this_result$j_usage);dev.off()
  pdf(paste0(this_sample,".cdr3aa_length_usage.pdf"))
  plot_usage(this_result$cdr3aa_length_usage);dev.off()

  plot_cdr3aa_bar(this_result$cdr3aa_length_v, 'V segment' ,
                  file_out =  paste0(this_sample,".cdr3aa_length_v.pdf"))
  plot_cdr3aa_bar(this_result$cdr3aa_length_cdr3aa, 'CDR aa',
                  file_out =  paste0(this_sample,".cdr3aa_length_cdr3aa.pdf"))
  plot_cdr3_stat(this_result$cdr3aa_stat,
                 file_out = paste0(this_sample,".cdr3aa_stat.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'circle',
                       file_out = paste0(this_sample,".v_j_circle.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'bubble',
                       file_out = paste0(this_sample,".v_j_bubble.pdf"))
})


all_results_IgG <- lapply(keep_IRdata,function(x){
  x=subset(x,type='IgG')
  stat_IR_basic(x)
})
lapply(1:length(all_results_IgG), function(i){
  this_result <- all_results_IgG[[i]]
  this_sample <- names(all_results_IgG)[i]
  this_sample <- paste0(this_sample,".IgG")
  pdf(paste0(this_sample,".v_usage.pdf"))
  plot_usage(this_result$v_usage);dev.off()
  pdf(paste0(this_sample,".d_usage.pdf"))
  plot_usage(this_result$d_usage);dev.off()
  pdf(paste0(this_sample,".j_usage.pdf"))
  plot_usage(this_result$j_usage);dev.off()
  pdf(paste0(this_sample,".cdr3aa_length_usage.pdf"))
  plot_usage(this_result$cdr3aa_length_usage);dev.off()

  plot_cdr3aa_bar(this_result$cdr3aa_length_v, 'V segment' ,
                  file_out =  paste0(this_sample,".cdr3aa_length_v.pdf"))
  plot_cdr3aa_bar(this_result$cdr3aa_length_cdr3aa, 'CDR aa',
                  file_out =  paste0(this_sample,".cdr3aa_length_cdr3aa.pdf"))
  plot_cdr3_stat(this_result$cdr3aa_stat,
                 file_out = paste0(this_sample,".cdr3aa_stat.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'circle',
                       file_out = paste0(this_sample,".v_j_circle.pdf"))
  plot_v_j_combination(this_result$vj_usage_matrix,image_type = 'bubble',
                       file_out = paste0(this_sample,".v_j_bubble.pdf"))
})

save(all_results,all_results_IgA,all_results_IgG,all_results_IgM,file='analysis_result.Rdata')
```


## compare the v/j/usage and between case and control group 





